---
title: "Life Expectancy"
output: html_notebook
---

Installing Packages
```{r}
#install.packages("tidyverse")
```

Setting Libraries
```{r}
library(tidyverse)
```

Loading in the Dataset
```{r}
life <- read.csv("life expectancy.csv")
life
```

Getting the summary statistics 
```{r}
summary(life)
```

# Hypothesis 1: Impact of Expenditure on Health and Education on Life Expectancy
```{r}
hyp1 <- ggplot(life, aes(x = Health.Expenditure.., y = Education.Expenditure.., color = Life.Expectancy.World.Bank)) +
  geom_point() +
  labs(x = "Health Expenditure (% of GDP)",
       y = "Education Expenditure (% of GDP)",
       title = "Impact of Government Expenditure on Life Expectancy",
       color = "Life Expectancy")
hyp1
```
With Trend Line
```{r}
hyp1trend <- ggplot(life, aes(x = Health.Expenditure.., y = Education.Expenditure.., color = Life.Expectancy.World.Bank)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, aes(group = 1)) +
  labs(x = "Health Expenditure (% of GDP)",
       y = "Education Expenditure (% of GDP)",
       title = "Impact of Government Expenditure on Life Expectancy",
       color = "Life Expectancy")
hyp1trend
```

Life Expectancy by Income Group.
This graph is mostly here to show the change in time of life expectancy among income brackets, to give more nuance
to the above graph.
```{r}
hyp1income <- ggplot(life, aes(x = Year, y = Life.Expectancy.World.Bank, group = IncomeGroup, color = IncomeGroup)) +
  geom_line() +
  facet_wrap(~IncomeGroup, scales = "free_y") +
  labs(x = "Year",
       y = "Life Expectancy",
       color = "Income Group",
       title = "Life Expectancy by Income Group") 
hyp1income
```

# Hypothesis 2: Prevalence of Undernourishment and Communicable Disease on Life Expectancy
Factoring by Life Expectancy
```{r}
hyp2 <- ggplot(life, aes(x = Prevelance.of.Undernourishment, y = Communicable, color = Life.Expectancy.World.Bank)) +
  geom_point() +
  labs(x = "Prevalence of Undernourishment",
       y = "Communicable Disease",
       title = "Malnourishment and Communicable Dieseases vs. Life Expectancy",
       color = "Life Expectancy")
hyp2
```

Factoring by Region
```{r}
hyp2region <- ggplot(life, aes(x = Prevelance.of.Undernourishment, y = Communicable, color = Region)) +
  geom_point() +
  labs(x = "Prevalence of Undernourishment",
       y = "Communicable Disease",
       title = "Malnourishment and Communicable Dieseases vs. Global Region",
       color = "Region")
hyp2region
```

# Hypothesis 3: Impact of Disability-Adjusted Life Years and Unemployment Rate on Life Expectancy
```{r}
hyp3 <- ggplot(life, aes(x = Unemployment, y = Injuries, color = Life.Expectancy.World.Bank)) +
  geom_point() +
  labs(x = "Unemployment Rate",
       y = "Disability Adjusted Life Years (DALYs)",
       title = "DALY's and Unemployment",
       color = "Life Expectancy")
hyp3
```

# Hypothesis 4: Increase in CO2 Emissions and its Effect on Life Expectancy 
We also take a look at which regions in general are the ones with the highest CO2 emissions
```{r}
hyp4 <- ggplot(life, aes(x = CO2, y = Life.Expectancy.World.Bank, color = Region)) +
  geom_point() +
  labs(x = "CO2 Emissions",
       y = "Life Expectancy",
       title = "CO2 Emissions and Life Expectancy, by Region",
       color = "World Region")
hyp4
```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

